Report and analysis on implementation of IMM algorithm for multiple-model dynamics tracking

### 2020-02-02 Latex/draft.tex

\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath} % Advanced math typesetting
\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage[english]{babel} % Change hyphenation rules
\usepackage{hyperref} % Add a link to your document
\usepackage{graphicx} % Add pictures to your document
\usepackage{listings} % Source code formatting and highlighting
\usepackage{bookmark}
\usepackage{natbib}
\usepackage{geometry}
\usepackage{bbm}
%\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}
\usepackage{adjustbox}
\usepackage{subcaption}
% \pagestyle{fancy}
% \fancyhf{}
% \fancyhead[LE,RO]{Overleaf}
% \fancyhead[RE,LO]{Guides and tutorials}
% \fancyfoot[CE,CO]{\leftmark}
% \fancyfoot[LE,RO]{\thepage}
\graphicspath{ {Immagini/} }
%C:\Users\erikz\OneDrive\Desktop\PaioPaio2\IMM-Sensors-Network\Latex\Immagini
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

@@

@@

Following is a short recap of the algorithm, to see it in much more detail refer to CITA QUA

@@

\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 2: consensus rate = 2}       \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.6709        & 3.2770       & 8.4954      \\
                \hline
                % R1,Q2           & 0.1132                &  0.2847           & 0.6577                      \\
                % \hline
                R2,Q1     & 0.1392        & 0.6907       & 2.0562      \\
                % \hline
                % R2,Q2           & 0.0539                & 0.1454             & 0.2334                   \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.07629       & 2.5799       & 9.3296      \\
                % \hline
                % R1,Q2        & 0.1664                & 0.2726                & 1.0990              \\
                \hline
                R2,Q1     & 0.1585        & 0.5868       & 2.1211      \\
                %     \hline
                %     R2,Q2           & 0.0804                & 0.0947            & 0.4190                   \\
                % \hline
            \end{tabular} $}
\end{center}

@@

What we gather from these tables is that, specifically in the case of the unicycle $\mathbbm{M}_{2}$ (that is a more complex model set), 
a consensus computed at a high frequency (rate=1, rate=2) gives disastrous results with any magnitude of noise. This is probably caused by 
the nature of the IMM algorithm that gets impeded by the consensus which homogenizes the internal Kalman filters input to a point which 
the IMM can't compute their probabilities efficiently. In fact we see a much better results with lower frequency such as rate=10 and rate=20.
We also tried the case in which we do not compute any consensus and we let individual sensors work alone and, while we see good results, 
it doesn't seem to be the best compromise.
\\
In the case of the Random Walk with a rate=2 we have good results with low $R$, but the algorithm is really sensible to changes to this 
parameter and performs really bad with $R1$.
\\
While we see that with both model sets the case with rate=20 gives very good results, but we also notice that the maximum of both the individual 
IMMs and of the consensus can get pretty high so if we have an application where the frequency of estimation must be high and we can't 
have a big overshoot, then this rate can fail.
All things considered the best trade-off may be the rate=10, which always gives good results and has double the frequency of rate=20.
\\
Following are some graphs of the best and worst cases computed by the simulations. More graphs and a video of the algorithm working can 
be found at ...

\end{document}

>>>>

\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath} % Advanced math typesetting
\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage[english]{babel} % Change hyphenation rules
\usepackage{hyperref} % Add a link to your document
\usepackage{graphicx} % Add pictures to your document
\usepackage{listings} % Source code formatting and highlighting
\usepackage{bookmark}
%\usepackage{natbib}
\usepackage{geometry}
\usepackage{bbm}
%\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}
\usepackage{adjustbox}
\usepackage{subcaption}
% \pagestyle{fancy}
% \fancyhf{}
% \fancyhead[LE,RO]{Overleaf}
% \fancyhead[RE,LO]{Guides and tutorials}
% \fancyfoot[CE,CO]{\leftmark}
% \fancyfoot[LE,RO]{\thepage}
\graphicspath{ {Immagini/} }
%C:\Users\erikz\OneDrive\Desktop\PaioPaio2\IMM-Sensors-Network\Latex\Immagini
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

@@

    \begin{tabular}{||c||c|c|}%{|width=\columnwidth|}

@@

Following is a short recap of the algorithm, to see it in much more detail refer to \textit{Interacting Multiple Model Methods in Target Tracking}  \cite{bar-shalomInteractingMultipleModel}

@@

\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 2: consensus rate = 2}       \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.6709        & 3.2770       & 8.4954      \\
                \hline
                % R1,Q2           & 0.1132                &  0.2847           & 0.6577                      \\
                % \hline
                R2,Q1     & 0.1392        & 0.6907       & 2.0562      \\
                % \hline
                % R2,Q2           & 0.0539                & 0.1454             & 0.2334                   \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.07629       & 2.5799       & 9.3296      \\
                % \hline
                % R1,Q2        & 0.1664                & 0.2726                & 1.0990              \\
                \hline
                R2,Q1     & 0.1585        & 0.5868       & 2.1211      \\
                %     \hline
                %     R2,Q2           & 0.0804                & 0.0947            & 0.4190                   \\
                 \hline
            \end{tabular} $}
\end{center}

@@

What we gather from these tables is that, specifically in the case of the unicycle $\mathbbm{M}_{2}$ (that is a more complex model set), 
a consensus computed at a high frequency (rate=1, rate=2) gives disastrous results with any magnitude of noise.
This is probably caused by the nature of the IMM algorithm that gets impeded by the consensus which homogenizes the internal Kalman filters input to a point which 
the IMM can't compute their probabilities efficiently. In fact we see a much better results with lower frequency such as rate=10 and rate=20.
We also tried the case in which we do not compute any consensus and we let individual sensors work alone and, while we see good results, 
it doesn't seem to be the best compromise.
\\
In the case of the Random Walk with a rate=2 we have good results with low $R$, but the algorithm is really sensible to changes to this 
parameter and performs really bad with $R1$.
\\
While we see that with both model sets the case with rate=20 gives very good results, but we also notice that the maximum of both the individual 
IMMs and of the consensus can get pretty high so if we have an application where the frequency of estimation must be high and we can't 
have a big overshoot, then this rate can fail.
All things considered the best trade-off may be the rate=10, which always gives good results and has double the frequency of rate=20.
\\
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/RMSIMMC2_20R2Q1.png}
    \caption{Case 1 at rate 1 : R2Q1}
    \label{fig:number}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/maxIMMC2_20R2Q1.png}
    \caption{Case 1 at rate 1 : Maximum with R2Q1}
    \label{fig:number}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/RMSIMMC2_1R1Q1.png}
    \caption{Case 2 at rate 1 : R1Q1}
    \label{fig:number}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/maxIMMC2_1R2Q1.png}
    \caption{Case 2 at rate 1 : Maximum with R2Q1}
    \label{fig:number}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/RMSIMMC2_10R2Q1.png}
    \caption{Case 2 at rate 10 : R2Q1}
    \label{fig:number}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/RMSnoconsC2R1Q2.png}
    \caption{Case 2 no consensus : R2Q1}
    \label{fig:number}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/RMSIMMC1_10R2Q1.png}
    \caption{Case 1 at rate 10 : R2Q1}
    \label{fig:number}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/IndvErroC1_10R2Q1.png}
    \caption{Case 1 at rate 10 : Individual Error R2Q1}
    \label{fig:number}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/RMSnoconsC1R2Q1.png}
    \caption{Case 1 no consensus : R2Q1}
    \label{fig:number}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.50\textwidth]{Immagini/Trajectory.png}
    \caption{A Typical Trajectory}
    \label{fig:number}
\end{figure}

Following are some graphs of the best and worst cases computed by the simulations. More graphs and a video of the algorithm working can 
be found at \href{https://github.com/PaioPaio/IMM-Sensors-Network/tree/no_speed_jumps/Graphs}{the project's GitHub}

\bibliography{bib} 
\bibliographystyle{ieeetr}
\end{document}
